Molecular transport in human pial perivasculature

### 2024-03-11 paper/main.tex
Make .tex compile outside of Overleaf.

 \documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{bm}
\usepackage{caption}
\usepackage{subcaption}
\graphicspath{{figures/}}

@@

\citet{hodneland2019new} developed a method to image the brains' microvasculature based on time-of-flight (ToF) and quantitative susceptibility mapping (QSM) to identify arterial and venous networks.
We derive a detailed tetrahedral mesh of both the parenchyma and the surrounding CSF-filled spaces alongside a network representation of the vasculature from the anatomical data provided therein.

@@

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.33\textwidth}
         \centering
         \includegraphics[width=\textwidth]{paper/figures/modelA_total_conc.png}
         \caption{arterial inflow, pure diffusion}
         \label{fig:y equals x}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.33\textwidth}
         \centering
         \includegraphics[width=\textwidth]{paper/figures/modelB_total_conc.png}
         \caption{SAS inflow, pure diffusion}
         \label{fig:three sin x}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.33\textwidth}
         \centering
         \includegraphics[width=\textwidth]{paper/figures/modelC_total_conc.png}
         \caption{arterial inflow, diffusion + PVS convection}
         \label{fig:five over x}
     \end{subfigure}
        \caption{Total tracer amount in parenchyma, CSF, arterial PVS and venous PVS}
        \label{fig:three graphs}
\end{figure}

>>>>

 \documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{bm}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{natbib}
\graphicspath{{figures/}}

@@

\cite{hodneland2019new} developed a method to image the brains' microvasculature based on time-of-flight (ToF) and quantitative susceptibility mapping (QSM) to identify arterial and venous networks.
We derive a detailed tetrahedral mesh of both the parenchyma and the surrounding CSF-filled spaces alongside a network representation of the vasculature from the anatomical data provided therein.

@@

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.33\textwidth}
         \centering
         \includegraphics[width=\textwidth]{modelA_total_conc.png}
         \caption{arterial inflow, pure diffusion}
         \label{fig:y equals x}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.33\textwidth}
         \centering
         \includegraphics[width=\textwidth]{modelB_total_conc.png}
         \caption{SAS inflow, pure diffusion}
         \label{fig:three sin x}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.33\textwidth}
         \centering
         \includegraphics[width=\textwidth]{modelC_total_conc.png}
         \caption{arterial inflow, diffusion + PVS convection}
         \label{fig:five over x}
     \end{subfigure}
        \caption{Total tracer amount in parenchyma, CSF, arterial PVS and venous PVS}
        \label{fig:three graphs}
\end{figure}
